Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-24 manuscript.Rmd
five things

In this paper, we present an inertial sensing method to classify infant body position from moment-to-moment across an entire day, and validate its accuracy using XX hours of video recorded across XX in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders such as the LENA device. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief sessions [CITES], the current investigation takes a needed step forward by testing accuracy over long recordings.

@@

Long-form audio recordings have had a transformational impact on language development by allowing researchers to characterize opportunities for learning in daily life. Measuring the amount of speech heard by infants in the home [@Weisleder2013] or in a daycare setting [@PerryPrince2018] revealed individual differences input that predict later vocabulary. Full-day language recording synchronized with other data sources allows researchers to identify how vocal input and production interacts with other processes. Beyond individual differences in aggregated data, long-form recordings can be used to determine the temporal schedule of experiences. For example, infants' daily experiences hearing music are clustered in time, with "bursty" episodes of hearing music separated by relatively long periods during which music is absent [@MendozaFausey2022]. Synchronizing audio recordings with other data sources extends researchers' ability to characterize daily experiences. Linking LENA&reg; speech measurements to repeated, time-stamped text-message surveys about infant device placement revealed that infants heard less caregiver speech during moments that they were restrained in devices such as swings, exersaucers, and car seats [@MalachowskiSalo2023]. A custom-built wearable ECG and audio recorder allowed @WassPhillips2022 to discover that infant arousal increases the likelihood of infant vocalization across the day. The ability to record real-time, synchronized data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within in an individual as opposed to comparisons of aggregated data between infants.

Key features
- unobtrusive (Bergelson; CTL stuff)
- mobile (no limits to where recording happens)
- real time
- long duration (capture entire day and heterogeniety in activities)
- automatic classification with good-enough accuracy (scaling)

>>>>

In this paper, we present an inertial sensing method to classify infant body position from moment-to-moment across an entire day, and validate its accuracy using XX hours of video recorded across XX in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features that should be replicated in long-form recordings of motor behavior [CITES]. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief sessions [CITES], the current investigation takes a needed step forward by testing accuracy over long recordings.

@@

Long-form audio recordings have had a transformational impact on language development by allowing researchers to characterize opportunities for learning in daily life. Measuring the amount of speech heard by infants in the home [@Weisleder2013] or in a daycare setting [@PerryPrince2018] revealed individual differences input that predict later vocabulary. Full-day language recording synchronized with other data sources allows researchers to identify how vocal input and production interacts with other processes. Beyond individual differences in aggregated data, long-form recordings can be used to determine the temporal schedule of experiences. For example, infants' daily experiences hearing music are clustered in time, with "bursty" episodes of hearing music separated by relatively long periods during which music is absent [@MendozaFausey2022]. Synchronizing audio recordings with other data sources extends researchers' ability to characterize daily experiences. Linking LENA&reg; speech measurements to repeated, time-stamped text-message surveys about infant device placement revealed that infants heard less caregiver speech during moments that they were restrained in devices such as swings, exersaucers, and car seats [@MalachowskiSalo2023]. A custom-built wearable ECG and audio recorder allowed @WassPhillips2022 to discover that infant arousal increases the likelihood of infant vocalization across the day.

We identified five key features of long-form audio methods to replicate in analagous studies of motor behavior. First, wearable audio recorders are *mobile*. Measurement is not limited to a particular room because the recording device travels with the participant. Data are stored on device, so participants do not need to be in range of a receiver. Second, wearable audio recording is *unobtrusive*. Participants' reactivity to observation, such as from a video camera, may influence behavior. For example, caregivers spoke more frequently to infants during a video-recorded portion of a home recording compared with audio-only segments captured by a LENA&reg; device [@Bergelson2019Input]. Third and fourth, recordings capture *real-time data* over a *full day*. The ability to record real-time data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within in an individual as opposed to comparisons of aggregated data between infants. Synchronizing real-time data to other data streams helps to reveal sources of variability within an individual. Full-day recordings are essential for capturing experiences across the heterogeniety of daily routines that moderate behavior (e.g., play, feeding, errands) [CITE]. Burstiness of behavior means that long recordings are needed to capture clusters of events amid long periods in which they may be absent [@BarbaroFausey2022; @WarlaumontSobowale2021].

- automatic classification with good-enough accuracy (scaling)

### 2023-02-24 manuscript.tex
five things

In this paper, we present an inertial sensing method to classify infant body position from moment-to-moment across an entire day, and validate its accuracy using XX hours of video recorded across XX in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders such as the LENA device. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief sessions {[}CITES{]}, the current investigation takes a needed step forward by testing accuracy over long recordings.

@@

Impactful findings (Hailey write this paragraph)
- individual differences in experiences
- distribution of experiences (burstiness)
Full-day language recording synchronized with other data sources allows researchers to identify how vocal input and production interacts with other processes. Linking LENA® speech measurements to repeated, time-stamped text-message surveys about infant device use revealed that infants heard less caregiver speech during moments that they were restrained in devices such as swings, exersaucers, and car seats (Malachowski et al., 2023). A custom-built wearable ECG and audio recorder allowed Wass et al. (2022) to discover that infant arousal increases the likelihood of infant vocalization across the day. In both examples, the ability to record real-time, synchronized data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within in an individual as opposed to comparisons of aggregated data between infants.

Key features
- unobtrusive (Bergelson; CTL stuff)
- mobile (no limits to where recording happens)
- real time
- long duration (capture entire day and heterogeniety in activities)
- automatic classification with good-enough accuracy (scaling)

@@

@@

@@

@@

>>>>

In this paper, we present an inertial sensing method to classify infant body position from moment-to-moment across an entire day, and validate its accuracy using XX hours of video recorded across XX in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features that should be replicated in long-form recordings of motor behavior {[}CITES{]}. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief sessions {[}CITES{]}, the current investigation takes a needed step forward by testing accuracy over long recordings.

@@

The LENA® recorder is a commercial device that is worn by infants in a custom shirt pocket that has sufficient battery life and storage to record for an entire day. Closed-source LENA® algorithms analyze the audio recordings to provide counts of useful metrics, such as the number of words spoken by adults in the vicinity of the participant. Other long-form audio methods rely on custom-built recorders (Wass et al., 2022), apply alternative classification algorithms to LENA® data (Micheletti et al., 2022; Räsänen et al., 2020), or manually transcribe audio recorded by LENA® devices to improve accuracy or identify behaviors beyond the built-in categories (Bergelson, Casillas, et al., 2019; Mendoza \& Fausey, 2021).

Long-form audio recordings have had a transformational impact on language development by allowing researchers to characterize opportunities for learning in daily life. Measuring the amount of speech heard by infants in the home (Weisleder \& Fernald, 2013) or in a daycare setting (Perry et al., 2018) revealed individual differences input that predict later vocabulary. Full-day language recording synchronized with other data sources allows researchers to identify how vocal input and production interacts with other processes. Beyond individual differences in aggregated data, long-form recordings can be used to determine the temporal schedule of experiences. For example, infants' daily experiences hearing music are clustered in time, with ``bursty'' episodes of hearing music separated by relatively long periods during which music is absent (Mendoza \& Fausey, 2022). Synchronizing audio recordings with other data sources extends researchers' ability to characterize daily experiences. Linking LENA® speech measurements to repeated, time-stamped text-message surveys about infant device placement revealed that infants heard less caregiver speech during moments that they were restrained in devices such as swings, exersaucers, and car seats (Malachowski et al., 2023). A custom-built wearable ECG and audio recorder allowed Wass et al. (2022) to discover that infant arousal increases the likelihood of infant vocalization across the day.

We identified five key features of long-form audio methods to replicate in analagous studies of motor behavior. First, wearable audio recorders are \emph{mobile}. Measurement is not limited to a particular room because the recording device travels with the participant. Data are stored on device, so participants do not need to be in range of a receiver. Second, wearable audio recording is \emph{unobtrusive}. Participants' reactivity to observation, such as from a video camera, may influence behavior. For example, caregivers spoke more frequently to infants during a video-recorded portion of a home recording compared with audio-only segments captured by a LENA® device (Bergelson, Amatuni, et al., 2019). Third and fourth, recordings capture \emph{real-time data} over a \emph{full day}. The ability to record real-time data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within in an individual as opposed to comparisons of aggregated data between infants. Synchronizing real-time data to other data streams helps to reveal sources of variability within an individual. Full-day recordings are essential for capturing experiences across the heterogeniety of daily routines that moderate behavior (e.g., play, feeding, errands) {[}CITE{]}. Burstiness of behavior means that long recordings are needed to capture clusters of events amid long periods in which they may be absent (Barbaro \& Fausey, 2022; Warlaumont et al., 2021).

\begin{itemize}
\tightlist
\item
  automatic classification with good-enough accuracy (scaling)
\end{itemize}

@@

\leavevmode\vadjust pre{\hypertarget{ref-BarbaroFausey2022}{}}%
Barbaro, K. de, \& Fausey, C. M. (2022). Ten lessons about infants' everyday experiences. \emph{Current Directions in Psychological Science}, \emph{31}(1), 28--33. \url{https://doi.org/10.1177/09637214211059536}

\leavevmode\vadjust pre{\hypertarget{ref-Bergelson2019Input}{}}%
Bergelson, E., Amatuni, A., Dailey, S., Koorathota, S., \& Tor, S. (2019). Day by day, hour by hour: Naturalistic language input to infants. \emph{Developmental Science}, \emph{22}, e12715.

\leavevmode\vadjust pre{\hypertarget{ref-Bergelson2019Corpus}{}}%
Bergelson, E., Casillas, M., Soderstrom, M., Seidl, A., Warlaumont, A. S., \& Amatuni, A. (2019). What do {N}orth {A}merican babies hear? {A} large-scale cross-corpus analysis. \emph{Developmental Science}, \emph{22}, e12724.

@@

\leavevmode\vadjust pre{\hypertarget{ref-MendozaFausey2021}{}}%
Mendoza, J. K., \& Fausey, C. M. (2021). Everyday music in infancy. \emph{Developmental Science}, \emph{24}(6). \url{https://doi.org/10.1111/desc.13122}

\leavevmode\vadjust pre{\hypertarget{ref-MendozaFausey2022}{}}%
Mendoza, J. K., \& Fausey, C. M. (2022). Everyday parameters for episode-to-episode dynamics in the daily music of infancy. \emph{Cognitive Science}, \emph{46}(8). \url{https://doi.org/10.1111/cogs.13178}

\leavevmode\vadjust pre{\hypertarget{ref-MichelettiYao2022}{}}%
Micheletti, M., Yao, X., Johnson, M., \& Barbaro, K. de. (2022). Validating a model to detect infant crying from naturalistic audio. \emph{Behavior Research Methods}. \url{https://doi.org/10.3758/s13428-022-01961-x}

\leavevmode\vadjust pre{\hypertarget{ref-PerryPrince2018}{}}%
Perry, L. K., Prince, E. B., Valtierra, A. M., Rivero-Fernandez, C., Ullery, M. A., Katz, L. F., Laursen, B., \& Messinger, D. S. (2018). A year in words: The dynamics and consequences of language experiences in an intervention classroom. \emph{{PLOS} {ONE}}, \emph{13}(7), e0199893. \url{https://doi.org/10.1371/journal.pone.0199893}

\leavevmode\vadjust pre{\hypertarget{ref-RasanenSeshadri2020}{}}%
Räsänen, O., Seshadri, S., Lavechin, M., Cristia, A., \& Casillas, M. (2020). {ALICE}: An open-source tool for automatic measurement of phoneme, syllable, and word counts from child-centered daylong recordings. \emph{Behavior Research Methods}, \emph{53}(2), 818--835. \url{https://doi.org/10.3758/s13428-020-01460-x}

@@

\leavevmode\vadjust pre{\hypertarget{ref-WarlaumontSobowale2021}{}}%
Warlaumont, A. S., Sobowale, K., \& Fausey, C. M. (2021). Daylong mobile audio recordings reveal multitimescale dynamics in infants' vocal productions and auditory experiences. \emph{Current Directions in Psychological Science}, \emph{31}(1), 12--19. \url{https://doi.org/10.1177/09637214211058166}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Weisleder2013}{}}%
Weisleder, A., \& Fernald, A. (2013). Talking to children matters: Early language experience strengthens processing and builds vocabulary. \emph{Psychological Science}, \emph{24}, 2143--2152.
